---
title: "Pollution Indices by World Region"
author: "Jeremy Diaz"
date: "August 29, 2017"
output: html_document
---

### The Web Scraping

The pollution index data is taken from: https://www.numbeo.com/pollution/rankings_by_country.jsp. To learn more about their pollution index see: https://www.numbeo.com/pollution/indices_explained.jsp.

```{r setup, message = FALSE}


# Packages
library(rvest)
library(dplyr)
library(ggplot2)


# Data table URL to scrape
url <- "https://www.numbeo.com/pollution/rankings_by_country.jsp"


# Get the table as a R data.frame
pollution_df <- read_html(url) %>%
  html_nodes("table") %>%
  .[4] %>%
  html_table(fill = TRUE, header = 1) %>%
  as.data.frame()


```

Some intermediate processing is then done to assign each country to its respective world region: Asia, Africa, America, Europe, or Oceania.

```{r processing, echo = FALSE}


# Remove rank column
pollution_df <- dplyr::select(pollution_df,
                              -Rank)


# Assign the countries to Asia
Asia <- c("Mongolia", "Myanmar", "Bangladesh", "Vietnam", "China", "Lebanon",
          "Nepal", "Jordan", "Iran", "Pakistan", "India", "Bahrain", "Kazakhstan",
          "Saudi Arabia", "Georgia", "Thailand", "Qatar", "Philippines", "Turkey",
          "Hong Kong", "Malaysia", "Taiwan", "Israel", "Sri Lanka", "Indonesia", 
          "Cyprus", "United Arab Emirates", "South Korea", "Japan", "Singapore") %>%
  as.data.frame()

Asia$Region <- rep("Asia", length(Asia))


# Assign the countries to Africa
Africa <- c("Egypt", "Nigeria", "Kenya", "Morocco", "Algeria", "Tunisia",
            "South Africa", "Mauritius") %>%
  as.data.frame()

Africa$Region <- rep("Africa", length(Africa))


# Assign the countries to N and S America
America <- c("Peru", "Dominican Republic", "Venezuela", "Jamaica", "Chile",
             "Mexico", "Colombia", "Brazil", "Ecuador", "Argentina", "Uruguay",
             "Costa Rica", "United States", "Canada") %>%
  as.data.frame()

America$Region <- rep("America", length(America))


# Assign the countries to Europe
Europe <- c("Monaco", "Macedonia", "Albania", "Malta", "Ukraine", "Russia",
            "Bulgaria", "Bosnia And Herzegovina", "Serbia", "Greece", 
            "Italy", "Romania", "Poland", "Belgium", "Hungary", "Slovakia",
            "Czech Republic", "France", "Spain", "Belarus", "United Kingdom",
            "Lithuania", "Latvia", "Croatia", "Portugal", "Ireland", "Netherlands",
            "Germany", "Slovenia", "Denmark", "Austria", "Switzerland", "Norway",
            "Sweden", "Estonia", "Finland", "Iceland") %>%
  as.data.frame()

Europe$Region <- rep("Europe", length(Europe))


# Assign the countries to Oceania
Oceania <- c("Australia", "New Zealand") %>%
  as.data.frame()

Oceania$Region <- rep("Oceania", length(Oceania))


# Combine the data.frames
all_df <- rbind(Africa, America, Asia, Europe, Oceania)


# Match the World Region-Country matched data.frame to the
# Pollution index-Country matched data.frane
all_df$poll_ind <- pollution_df$Pollution.Index[match(all_df$.,
                                                      pollution_df$Country)]


```

### The Visualization

Now we can produce a vibrant scatter plot of the data. The large grey squares represent the average value of each region.

```{r plot}


# Plot it
ggplot(all_df,
       aes(x = Region,
           y = poll_ind,
           fill = Region)) +
  theme_bw() +
  stat_summary(aes(y = poll_ind, group = 1),
               fun.y = mean, 
               group = 1,
               geom = "point",
               size = 17,
               shape = 22,
               col = "black",
               fill = "grey") +
  geom_jitter(width = 0.05,
              height = 0.05,
              size = 5,
              pch = 21,
              col = "black") +
  labs(y = "Pollution Index Value",
       x = "",
       title = "Pollution Indices by World Region",
       subtitle = "Data from: https://www.numbeo.com/pollution/rankings_by_country.jsp") +
  viridis::scale_fill_viridis(discrete = TRUE) +
  theme(plot.title = element_text(hjust = 0.5, size = 18),
        plot.subtitle = element_text(hjust = 0.5, size = 10),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title = element_text(size = 14),
        aspect.ratio = 8.5/11) +
  guides(fill = FALSE)


```


