---
title: "Peak in Bone Spur Searches after Executive Order 13223 Modification"
author: "Jeremy Diaz"
date: "October 21, 2017"
output: html_document
---

This visualization was inspired by the following reddit post (https://www.reddit.com/r/politics/comments/77o6oz/presidential_executive_order_amending_executive/donglor/), where a user joked that the "How to get bone spurs in feet?" search was going to reach a record high following President Trump's ammending of Executive Order 13223.

### Libraries Used

```{r setup}



library(gtrendsR)
library(ggplot2)



```

### The Gathering

Thankfully, the `gtrendsR` package makes getting Google hits (https://support.google.com/analytics/answer/6086082?hl=en) data extremely easy.

```{r GetGoogleHitsData}



# Get 'bone spurs' Google hits data
bone_spurs <- gtrends('bone spurs', time = 'now 7-d')$interest_over_time


# Format the date of USAToday article on EO modification
EO_article <- strptime("2017-10-20 16:18:00", format = '%Y-%m-%d %H:%M:%S')



```

### The Visualization

And... voilà! Turns out that the Google hits for 'bone spurs' did reach a weakly maximum following the news!

```{r TheFigure, fig.height = 6, fig.width = 6}



# Plot it
ggplot(bone_spurs,
       aes(x = date,
           y = hits)) +
  geom_vline(xintercept = EO_article,
             col = 'red', lwd = 1.25,
             alpha = 0.5) +
  geom_line(lwd = 1,
            col = 'black') +
  theme_minimal() +
  geom_text(aes(x = EO_article,
                y = 95),
            label = 'Executive\nOrder\n13223\nAmmended',
            hjust = 1.1, col = 'red') +
  labs(x = '', y = '',
       title = 'Bone Spurs Google Search Activity') +
  theme(aspect.ratio = 10/9,
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5, size = 16))



```


