---
title: "How Important are Individual South Park Characters?"
author: "Jeremy Diaz"
date: "August 29, 2017"
output: html_document
---

### The Web Scraping

First, get the Wikipedia page listing all South Park episodes. Then, scrape the plot description text from each episode's page, filtering to only proper nouns (the goal here is to get names). We then can get a count of the number of times each name appeared throughout all episode plot descriptions.

```{r setup, message = FALSE}


# Packages
library(rvest)
library(ggplot2)


# Get the wikipedia URL for all the episodes
url <- "https://en.wikipedia.org/wiki/List_of_South_Park_episodes"


# Scrape the URLs for all episodes
episode_urls <- read_html(url) %>%
  html_nodes(".summary a") %>%
  html_attr("href")


# Create an empty vector to fill
synopses <- c()


# Get all the plot descriptions
for (i in 1:279) {
  
  # Complete the URL
  # Get the plot description
  # And only text
  intermediate <- read_html(paste("https://en.wikipedia.org", episode_urls[i], sep = "")) %>%
    html_nodes("p") %>%
    html_text()
  
  # Append each episode's description to the empty vector
  synopses <- append(synopses, intermediate)
  
}


# Get only the proper nouns
synopsis <- gsub("[^a-zA-Z ]", " z ", synopses)

synopsis <- paste(synopsis, collapse = "") %>%
  strsplit(split = " ") %>%
  .[[1]]

ind <- grep("[A-Z]", synopsis)

synopsis <- synopsis[ind]

merge_ind <- ind[2:length(ind)] - ind[1:length(ind) - 1] == 1

for (i in length(synopsis):2) {
  if (merge_ind[i - 1]) {
    synopsis[i - 1] <- paste(synopsis[i - 1],synopsis[i], sep = " ")
    synopsis[i] <- ""
  }
}

synopsis <- synopsis[synopsis != ""]


# Get a count of unique mentions
noun_table <- table(synopsis) %>%
  as.data.frame()


```

After that, there is a lot of filtering to do; this consists of removing capitalized words which appear in the top 25 for 'number of counts', until only South Park character names remain. 

```{r filtering, echo = FALSE}


# Now get the top 20, removing irrelevant ones
noun_table_filt <- dplyr::filter(noun_table,
                                 synopsis != "The")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "South Park")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Parker")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Stone")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "In")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Comedy Central")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Mr")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "United States")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "It")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "He")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Trey Parker")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "The")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "They")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "American")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "DVD")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "I")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "This")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "However")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Meanwhile")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Matt Stone")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "After")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "When")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "IGN")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "A")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "TV")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "As")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Like")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "At")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Christmas")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Club")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "March")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "V")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "During")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "The A")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "April")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "November")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "While")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "October")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Dr")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "We")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Internet")
noun_table_filt <- dplyr::filter(noun_table_filt,
                                 synopsis != "Ms")


```

### The Visualization

Now, all that remains is some basic processing, and, voila, we now have an empirically-determined ranking for the importance of the top-25 South Park characters.

```{r pressure}


# Order the noun table
noun_table_filt <- noun_table_filt[with(noun_table_filt,
                                        order(-Freq, synopsis)), ]


# Get only the top 25
noun_table_filt <- noun_table_filt[1:25, ]


# Make the name a factor
noun_table_filt$synopsis <- factor(noun_table_filt$synopsis)


# Plot the results
ggplot(noun_table_filt,
       aes(y = Freq,
           x = reorder(synopsis,
                       Freq),
           fill = Freq)) +
  theme_bw() +
  geom_bar(stat = "identity",
           col = "black") +
  coord_flip() +
  scale_fill_continuous(high = "#006d2c",
                        low = "#B2E2E2") +
  guides(fill = FALSE) +
  ylab("Number of Name Appearances") +
  xlab("Character") +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 2100)) +
  ggtitle("How Important are South Park Characters?") +
  labs(subtitle = "Determined by how frequent their names appear in Wikipedia episode descriptions") +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 17),
        plot.subtitle = element_text(hjust = 0.5,
                                     size = 11),
        axis.title = element_text(size = 15),
        axis.text = element_text(size = 10))


```


